### 2021-07-21 doc/thesis/chapters/hls.tex
comments
move the entire section vhdl:testbench:general to hls:testbench:general

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Functions}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Loops}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Conditional Statements}

@@

An HLS testbench can be executed in different levels of abstraction, which is a major difference between a VHDL testbench and an HLS testbench.
The most important impact thereof is the execution speed - the time it takes to simulate a number of test cases on the DUT.\\

Section \ref{sec:hls:workflow} above already mentioned the topic of testbenches.
The following descriptions are a comprehensive extension around this topic and the simulation types.

>>>>

This section gives a brief overview of the \cplusplus\ HLS code style that is supported with Xilinx tools.
More detailed information can be found in the respective user guide \cite{VivadoUgHLS}.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interfaces}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimization}

%\subsection{Functions}
%\subsection{Loops}
%\subsection{Conditional Statements}

@@

The general significance of the simulation testbench for a HDL design is explained here, as well as the different levels of abstraction in which a HLS testbench can be executed.
These different levels of abstraction in the testbench execution are a major difference between a VHDL testbench and an HLS testbench.
The most important impact thereof is the execution speed - the time it takes to simulate a number of test cases on the DUT.\\

Section \ref{sec:hls:workflow} above already mentioned the topics of testbenches and simulation types.
The following descriptions shall be seen as a comprehensive extension around these topics.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{General}
\label{sub:hls:testbench:general}

In the development of software that runs on a CPU, the tool of step-by-step debugging is commonly used during the development process.
Various verification and testing libraries exist, in order to create unit tests, for example.
The advantage is, that the code that is developed there, can be compiled and run on the target CPU directly, while maintaining the direct instruction-by-instruction representation of the code.\\

However, in the development of hardware with any HDL, this is not possible.
HDL languages provide a syntax and semantic representation that allow to create parallel structures and a dependency on timing, such as a system clock.
The design is based on signals that perform logic operations and transfer values into registers.
Thus, HDL code is often called register-transfer level, or short, RTL code.
Before this code can be run on the target hardware, i.e. an FPGA, it needs to run through a process called synthesis.
In synthesis, the HDL code is translated into a netlist and is consequently mapped into hardware logic cells that are available in the target device.
Various optimizations are done during this process, so that the direct connection to the code representation is lost.
Additionally, it is impossible to access every single signal within the design during debugging on the hardware, which is probably also one of the main issues.
Synthesis tools like Xilinx Vivado provide support to make debugging possible in hardware, but require a large effort to implement them, especially in terms of synthesis time.
Another big factor that speaks against debugging in hardware generally, is that the process of synthesis takes a comparably large amount of time to transform code into the target technology.
Each time the code is adapted, the entire synthesis process needs to be started over again.
Because of all of these reasons, debugging HDL code step-by-step as in software is not possible.\\

Thus, in order to allow debugging and verification of HDL code, the technology of simulation was invented.
Here, the HDL is also translated into a netlist that represents all the parallel processes just like in hardware, but the subsequent step of synthesis is not taken.
Therefore, simulation comes to a result much faster.
Since HDL designs actually only consist of electrical wires and some basic block primitives, like flipflops or lookup tables, it is difficult to verify correct values.
They would need to be compared in their binary bit-pattern format, at the correct point in time.
Of course the HDL language provides support with different datatypes, that abstract the binary number representation and make the numbers human-readable.
However, it remains an enormous effort to manually write testing code to verify a bus interface, for example.
In order to simplify such complex operations, various testbench frameworks and libraries are available to developers.

### 2021-07-21 doc/thesis/chapters/implementation.tex
move the entire section vhdl:testbench:general to hls:testbench:general

The general significance of a simulation testbench in hardware description language (HDL) design is explained here, as well as an introduction to the used testbench framework that is used in this project.

%%%%%%%%%%%%%
\subsubsection{General}
\label{sub:VHDL:Testbench:General}

In the development of software that runs on a CPU, the tool of step-by-step debugging is commonly used during the development process.
Various verification and testing libraries exist, in order to create unit tests, for example.
The advantage is, that the code that is developed there, can be compiled and run on the target CPU directly, while maintaining the direct step-by-step representation of the code.\\

However, in the development of hardware with any HDL, this is not possible.
HDL languages provide a syntax and semantic representation that allow to create parallel structures and a dependency on timing, such as a system clock.
The design is based on signals that perform logic operations and transfer values into registers.
Thus, HDL code is often called register-transfer level, or short, RTL code.
Before this code can be run on the target hardware, i.e. an FPGA, it needs to run through a process called synthesis.
In synthesis, the HDL code is translated into a netlist and is consequently mapped into hardware logic cells that are available in the target device.
Various optimizations are done during this process, so that the direct connection to the code representation is lost.
Additionally, it is impossible to access every single signal within the design during debugging on the hardware, which is probably also one of the main issues.
Synthesis tools like Xilinx Vivado provide support to make debugging possible in hardware, but require a large effort to implement them, especially in terms of synthesis time.
Another big factor that speaks against debugging in hardware generally, is that the process of synthesis takes a comparably large amount of time to transform code into the target technology.
Each time the code is adapted, the entire synthesis process needs to be started over again.
Because of all of these reasons, debugging HDL code step-by-step as in software is not possible.\\

Thus, in order to allow debugging and verification of HDL code, the technology of simulation was invented.
Here, the HDL is also translated into a netlist that represents all the parallel processes just like in hardware, but the subsequent step of synthesis is not taken.
Therefore, simulation comes to a result much faster.
Since HDL designs actually only consist of electrical wires and some basic block primitives, like Flipflops or lookup tables, it is difficult to verify correct values.
They would need to be compared in their binary bit-pattern format, at the correct point in time.
Of course the HDL language provides support with different datatypes, that abstract the binary number representation and make the numbers human-readable.
However, it remains an enormous effort to manually write testing code to verify a bus interface, for example.
In order to simplify such complex operations, various testbench frameworks are available to developers.

@@

%%%%%%%%%%%%%
\subsubsection{Framework cocotb}
\label{sub:VHDL:FrameworkCocotb}

>>>>

The HDL compiler and the testbench framework that are used in this project are introduced here.

@@

%%%%%%%%%%%%%
\subsubsection{Testbench framework cocotb}
\label{sub:VHDL:FrameworkCocotb}
